---
title: "Example BO2"
output: html_notebook
---


```{r}
#library(hetGP, lib.loc = "/lcrc/project/EMEWS/bebop/R-packages/")
library(hetGP)
library(scales)
library(data.table)
library(lhs)
library(ggplot2)
library(mvtnorm)
library(tidyverse)
library(plotly)
source("analysis_helpers.R")
```

```{r}
experiment_tracker <- read.csv('experiment_tracker.csv')

df1 <- combine_results(experiment_tracker$out_file[1], 
                       experiment_tracker$experiment[1],
                       experiment_tracker$summary_file[1])
df2 <- combine_results(experiment_tracker$out_file[2], 
                       experiment_tracker$experiment[2],
                       experiment_tracker$summary_file[2])
df3 <- combine_results(experiment_tracker$out_file[3], 
                       experiment_tracker$experiment[3],
                       experiment_tracker$summary_file[3])

# combine
df <- rbind(df1, df2, df3)

ggplot(df) + 
  geom_line(aes(x=budget,y=y_std,color=experiment,group=experiment))+
  theme_minimal()
```

A bit more aggregated (by iteration, I guess)?
```{r}
ggplot(df %>% group_by(experiment, iter) %>% summarise(y_std_mean=mean(y_std))) + 
  geom_line(aes(x=iter, y=y_std_mean, color=experiment, group=experiment)) +
  theme_minimal()
```
```{r}
best_traj
```
```{r}
# update summary files to reflect new filepaths 
df$instance_dir <- gsub('1.0-adaptive_ts_1742217498.163954', '3K_hospitalizations', df$instance_dir)
df$instance_dir <- gsub('1.0-adaptive_ts_1742053883.049385', '2K_hospitalizations', df$instance_dir)

# grab output files for best trajectories found with each experiment
best_traj <- df %>%
                group_by(experiment) %>%
                select(experiment, y_std, instance_dir) %>%
                slice_min(y_std) %>%
                ungroup()
                

file_suffix <- '/output/counts_r1.csv'

traj1 = prepare_trajectories(paste0(best_traj$instance_dir[1],file_suffix), melted=TRUE)
traj1$experiment <- best_traj$experiment[1]
traj2 = prepare_trajectories(paste0(best_traj$instance_dir[2],file_suffix), melted=TRUE)
traj2$experiment <- best_traj$experiment[2]
traj3 = prepare_trajectories(paste0(best_traj$instance_dir[3],file_suffix), melted=TRUE)
traj3$experiment <- best_traj$experiment[3]
```


```{r}
ggplot(traj1) + 
  geom_line(aes(x=date, y=val, color=type, group=type)) +
  facet_wrap(~metric) +
  ggtitle(best_traj$experiment[1]) +
  theme_minimal()

ggplot(traj2) + 
  geom_line(aes(x=date, y=val, color=type, group=type)) +
  facet_wrap(~metric) +
  ggtitle(best_traj$experiment[2]) +
  theme_minimal()

ggplot(traj3) + 
  geom_line(aes(x=date, y=val, color=type, group=type)) +
  facet_wrap(~metric) +
  ggtitle(best_traj$experiment[3]) +
  theme_minimal()
```


Initial design:
```{r}
plot_initial_design <- function(df){
  
}
```

```{r}
fig01 <- plot_ly(out_df, x = ~seed, y = ~s2x, z = ~sah,
               marker = list(color = ~y_std, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>% add_markers()
fig02 <- plot_ly(out_df, x = ~seed, y = ~s2x, z = ~ba,
               marker = list(color = ~y_std, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>% add_markers()
fig03 <- plot_ly(out_df, x = ~seed, y = ~sah, z = ~ba,
               marker = list(color = ~y_std, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>% add_markers()
```


```{r}
fig1 <- plot_ly(out_df, x = ~seed, y = ~s2x, z = ~sah,
               marker = list(color = ~iter, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>% add_markers()
fig2 <- plot_ly(out_df, x = ~seed, y = ~s2x, z = ~ba,
               marker = list(color = ~iter, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>% add_markers()
fig3 <- plot_ly(out_df, x = ~seed, y = ~sah, z = ~ba,
               marker = list(color = ~iter, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>% add_markers()
```



```{r}
plot_ly(both3k_df %>% filter(iter==1, y_std<0), x = ~seed, y = ~s2x, z = ~sah, 
               marker = list(color = ~y_std, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE))
```



```{r}
# order by instance
both3k_summary <- both3k_summary[order(both3k_summary$instance),]

bounds = list(c(.01, .15), c(0.1, 1), c(0.01, 0.5))
            
unscale_params <- function(x, bounds){
  return((x - bounds[1]) / (bounds[2] - bounds[1]))
}


both3k_summary$s2xs <- unscale_params(both3k_summary$susceptible.to.exposed.probability, bounds[[1]])
both3k_summary$sahs <- unscale_params(both3k_summary$stay.at.home.probability, bounds[[2]])
both3k_summary$bas <- unscale_params(both3k_summary$stoe.behavioral.adjustment.probability, bounds[[3]])
```

```{r}
# can we just cbind these instead of merging?

both3k_dff <- cbind(both3k_df, both3k_summary)
```

```{r}
# make sure parameters are correct
tol <- 1e-3

mean((both3k_dff$s2x - both3k_dff$s2xs) < tol)
mean((both3k_dff$sah - both3k_dff$sahs) < tol)
mean((both3k_dff$ba - both3k_dff$bas) < tol)
mean((both3k_dff$seed - both3k_dff$seed) < tol)

# ok great we're good
```


```{r}
# get output files, ordered by objective (smallest to largest)
output_files <- both3k_dff[order(both3k_dff$y), 'instance_dir']

# look at best overall
output_file <- paste0(output_files[[1]], '/output/counts_r1.csv')
```


```{r}
source("analysis_helpers.R")
df_melted = prepare_trajectories(output_file, melted=TRUE)
```


```{r}
ggplot(df_melted) + 
  geom_line(aes(x=date, y=val, color=type, group=type)) +
  facet_wrap(~metric) +
  theme_minimal()
```


```{r}
  sim_df <- data.table::fread(output_file,
                              select = c("tick", "hosp_r_count", "hosp_icu_r_count",
                                         "hosp_d_count", "hosp_icu_d_count",
                                         "icu_r_count", "icu_d_count", "dead_count"))
  sim_df[, date := as.IDate("2020-03-16") + (tick / 24)]
  sim_df[, total_hosp_sim := hosp_r_count + hosp_icu_r_count +
           hosp_d_count + hosp_icu_d_count + icu_r_count + icu_d_count]
  
  ## process ground truth
  gt_d_df <- data.table::fread(gt_d_file)
  gt_h_df <- data.table::fread(gt_h_file)
  
  gt_d_df <- gt_d_df[(date >= start_date) & (date <= end_date)]
  gt_h_df <- gt_h_df[(date >= start_date) & (date <= end_date)]
  
  gt_d_df <- gt_d_df[!is.na(deaths)]
  gt_h_df <- gt_h_df[!is.na(tot.hosp)]
  
  ## merge
  df_all <- merge(sim_df, gt_h_df, by = "date", all.y = TRUE)
  df_all <- merge(df_all, gt_d_df, by = "date", all.x = TRUE)
  
  df_all[, err:= abs(tot.hosp - total_hosp_sim)/tot.hosp + abs(deaths - dead_count)/deaths]
  
  # melt for plots
  df_melted <- melt(
    df_all, 
    id.vars = c("date", "tick"), 
    measure.vars = c("total_hosp_sim", "tot.hosp", "dead_count", "deaths"),
    variable.name = "type_metric",
    value.name = "val"
  )
  
  # Create 'metric' and 'type' based on column names
  df_melted[, metric := fifelse(type_metric %in% c("tot.hosp", "total_hosp_sim"), "hosp", "deaths")]
  df_melted[, type := fifelse(type_metric %in% c("tot.hosp", "deaths"), "ground_truth", "simulation")]
  
  # Remove the original column name (type_metric) since it's encoded in `metric` and `type`
  df_melted[, type_metric := NULL]
```

```{r}
# round for merging 
both3k_summary[,c('s2x', 'sah', 'ba')] <- round(both3k_summary[,c('s2x', 'sah', 'ba')], 3)
both3k_df[,c('s2x', 'sah', 'ba')] <- round(both3k_df[,c('s2x', 'sah', 'ba')], 3)


both3k_instances <- merge(both3k_df, both3k_summary, by=c('s2x', 'sah', 'ba', 'seed'), all.x = TRUE)

both3k_instances <- both3k_instances[order(both3k_instances$budget),]

# check where merge didn't work
both3k_instances %>% filter(is.na(instance_dir))
```


```{r}
both3k_instances
```

```{r}
round(both3k_df[,c('s2x', 'sah', 'ba')],3)
```



```{r}
exp_path <- "/lcrc/project/EMEWS/improv/ncollier/repos/adaptiveTS/emews/experiments/3K_100gn_200nts_hosp_deaths_1.0-adaptive_ts_1742319512.630925/instances/"
instances <- as.numeric(
  gsub("instance_", "", list.dirs(exp_path, full.names = FALSE, recursive = FALSE))
)
  
extract_value <- function(lines, key) {
  match <- grep(paste0("^", key, "\\s*=\\s*"), lines, value = TRUE)
  if (length(match) == 0) return(NA)
  value <- sub(paste0("^", key, "\\s*=\\s*"), "", match)
  return(as.numeric(trimws(value)))
}

read_instance_params <- function(instance, exp_path){
  lines <- readLines(paste0(exp_path, 'instance_', instance, '/parameters_r1.txt'))
  params <- list(
    instance=instance,
    susceptible.to.exposed.probability = extract_value(lines, "susceptible.to.exposed.probability"),
    stay.at.home.probability = extract_value(lines, "stay.at.home.probability"),
    stoe.behavioral.adjustment.probability = extract_value(lines, "stoe.behavioral.adjustment.probability"),
    seed = extract_value(lines, "global.random.seed")
  )
  return(params)
}

#instance_params <- do.call(rbind, lapply(instances[3000:3014], read_instance_params, exp_path=exp_path))

for(i in seq_along(instances)){
  inst <- instances[[i]]
  read_instance_params(inst, exp_path)
}
```


```{r}
# Function to extract a value by matching key


# Extract values
susceptible_to_exposed_probability <- extract_value(lines, "susceptible.to.exposed.probability")
stay_at_home_probability <- extract_value(lines, "stay.at.home.probability")
stoe_behavioral_adjustment_probability <- extract_value(lines, "stoe.behavioral.adjustment.probability")
global_random_seed <- extract_value(lines, "global.random.seed")
```

### Setup
```{r}
# Read experiment config
#exp_path  <- "/lcrc/project/EMEWS/improv/abby/adaptiveTS/emews/experiments/big_experiment/results"
config <- fread("../emews/data/upfs/config.csv")
config[, (ncol(config)) := NULL]
config[, exp_id := as.numeric(gsub("exp_", "", exp_id))]

# Get true trajectory 
par_true <- c(0.45, 0.35, 50)
xtrue <- par_true[1:2]
strue <- par_true[3]
ytrue_sim <- run_sim(c(xtrue, strue))
ytrue <-  ytrue_sim$n_SI

ggplot(ytrue_sim) + 
  geom_line(aes(x=step, y=n_SI))+
  theme_minimal()
```


Run experiment 652 because it got killed on improv:
```{r}
library(pryr)
source('../script/R/adaptive_TS_seed.R')

ii <- 652
exp_path <- config$exp_path[ii]
exp_seed <- config$exp_seed[ii]
init_npar <- config$init_npar[ii]
nrep <- config$nrep[ii]
sim_budget <- config$sim_budget[ii]
grid_npar <- config$grid_npar[ii]
nTS_samp <- config$nTS_samp[ii]
p <- 2
ref <- -2

gc()  # Run garbage collection before measuring
mem_before <- mem_used()

out_adaptive_CRNGP_seed <- TSBatchBO_CRNGP_seed(init_npar, nrep, p, 
                                                sim_budget = sim_budget, 
                                                grid_npar = grid_npar, 
                                                nTS_samp = nTS_samp, 
                                                ytrue = ytrue_full, 
                                                sim_func = run_sim_err, 
                                                exp_seed = exp_seed, 
                                                covtype = "Matern5_2")

mem_after <- mem_used()

# Memory difference
mem_used_mb <- (mem_after - mem_before) / (1024^2)  # Convert bytes to MB
cat("Memory used by function: ", mem_used_mb, "MB\n")
```

```{r}
  X_01 <- lhs::randomLHS(n = init_npar, k = p)
  s <- 1:nrep
  Xs_01 <- cbind(X_01[rep(1:init_npar, each = nrep), ], rep(s, init_npar))
  
  y <- rep(NA, init_npar*nrep)
  for (ii in 1:(init_npar*nrep)){
    y[ii] <- run_sim_err(Xs_01[ii, ])$out
  }
```

### 1. "How quickly do we find N trajectories under threshold T"
- Need to identify reasonable thresholds
- What does "how quickly" mean in this context

```{r, fig.width=5}
out_list <- load_outputs(100, exp_path, config)
plot_thresholds(out_list, yobs)
plot_threshold_search(out_list, par_true)
```

```{r}
dfx <- search_space(out_list)

true_param <- data.frame(
  rep = par_true[3],  # x-coordinate
  p1 = par_true[1],  # y-coordinate
  p2 = par_true[2],  # z-coordinate
  iter = 1,
  method = "true"  # Custom label (if needed)
)

# Base 3D scatter plot
fig <- plot_ly(dfx, 
               x = ~rep, y = ~p1, z = ~p2, color = ~method, type = "scatter3d", mode = "markers") %>%
  add_trace(data = true_param, 
            x = ~rep, y = ~p1, z = ~p2, 
            type = "scatter3d", mode = "markers",
            marker = list(size = 10, color = "black", symbol = "square"),
            name = "true") %>%  # Custom legend label for the point
  layout(legend = list(
    x = 0.8, y = 0.5, xanchor = "left", yanchor = "middle"
  ))

fig
```

```{r}
dfx <- search_space(out_list)

true_param <- data.frame(
  rep = par_true[3],  # x-coordinate
  p1 = par_true[1],  # y-coordinate
  p2 = par_true[2],  # z-coordinate
  iter = 1,
  rmse=1,
  method = "true"  # Custom label (if needed)
)

# Base 3D scatter plot
fig <- plot_ly(dfx, 
               x = ~rep, y = ~p1, z = ~p2, color = ~rmse, type = "scatter3d", mode = "markers") %>%
  add_trace(data = true_param, 
            x = ~rep, y = ~p1, z = ~p2, 
            type = "scatter3d", mode = "markers",
            marker = list(size = 10, color = "black", symbol = "square"),
            name = "true") %>%  # Custom legend label for the point
  layout(legend = list(
    x = 0.8, y = 0.5, xanchor = "left", yanchor = "middle"
  ))

fig
```


```{r}
ggplot(dfx %>% filter(iter>1) %>% group_by(method, iter) %>% count()) + 
  geom_line(aes(x=iter, y=n, color=method, group=method))+
  theme_minimal()
```

```{r}
dfx <- search_space(out_list)

plot_ly(dfx, x = ~rep, y = ~p1, z = ~p2, color = ~method)
plot_ly(dfx %>% filter(method %in% c('adaptive_crn', 'fixed_crn')), x = ~rep, y = ~p1, z = ~p2, color = ~method)%>%   layout(legend = list(
    x = 0.8, y = 0.5, xanchor = "left", yanchor = "middle"
))
plot_ly(dfx %>% filter(method %in% c('adaptive_het', 'fixed_het')), x = ~rep, y = ~p1, z = ~p2, color = ~method)%>%   layout(legend = list(
    x = 0.8, y = 0.5, xanchor = "left", yanchor = "middle"
))
plot_ly(dfx %>% filter(method %in% c('adaptive_het', 'adaptive_crn')), x = ~rep, y = ~p1, z = ~p2, color = ~method)%>%   layout(legend = list(
    x = 0.8, y = 0.5, xanchor = "left", yanchor = "middle"
))
plot_ly(dfx %>% filter(method %in% c('fixed_het', 'fixed_crn')), x = ~rep, y = ~p1, z = ~p2, color = ~method)%>%   layout(legend = list(
    x = 0.8, y = 0.5, xanchor = "left", yanchor = "middle"
))
```


```{r message=FALSE, warning=FALSE}
exp_list <- 1:990
thresholds <- c(15, 20, 25, 30)
n4checkpoint <- c(10, 25, 50)

analysis_list <- lapply(exp_list, function(x) {
    analyze_experiment(x, exp_path=exp_path, config=config, thresholds=thresholds, n_trajectories=n4checkpoint)
})

# Assuming each `analyze_experiment` returns a list of 3 data frames,
# separate them by extracting each corresponding index
threshold_cnt <- do.call(rbind, lapply(analysis_list, `[[`, 1))
checkpoint_reached <- do.call(rbind, lapply(analysis_list, `[[`, 2))
threshold_budget_auc <- do.call(rbind, lapply(analysis_list, `[[`, 3))
threshold_budget_path <- do.call(rbind, lapply(analysis_list, `[[`, 4))
```



```{r message=FALSE, warning=FALSE}
ggplot(threshold_cnt, aes(x=factor(threshold), y=num_trajectories, fill=method)) + 
  #geom_bar(stat="summary", position="dodge") + 
  #geom_errorbar(stat='summary', position="dodge") +
  geom_boxplot() +
  facet_wrap(~sim_budget, ncol=1, 
             labeller = labeller(sim_budget = function(x) paste('budget=', x)), scales = "free_y")+
  xlab('Threshold (RMSE)') +
  ylab('Number trajectories found') +
  theme_minimal()

threshold_cnt$pct_traj <- threshold_cnt$num_trajectories/threshold_cnt$sim_budget

ggplot(threshold_cnt, aes(x=factor(threshold), y=pct_traj, fill=method)) + 
  #geom_bar(stat="summary", position="dodge") + 
  #geom_errorbar(stat='summary', position="dodge") +
  geom_boxplot() +
  xlab('Threshold (RMSE)') +
  ylab('Prop. of budget under threshold') +
  facet_wrap(~sim_budget, ncol=1, labeller = labeller(sim_budget = function(x) paste('budget=', x)))+
  theme_minimal()
```


Split by budget:
```{r}
threshold_cnt$method <- as.factor(threshold_cnt$method)

b200 <-  threshold_cnt %>% filter(sim_budget==200)
b500 <- threshold_cnt %>% filter(sim_budget==500)
b700 <- threshold_cnt %>% filter(sim_budget==700)
```


```{r}
b200 %>% 
  filter(threshold==30) %>%
  plot_ly() %>% 
  add_trace(x = ~as.numeric(method), y = ~pct_traj, type = "box", 
            hoverinfo = 'name+y',
            line = list(color = "black"),   # Black outline for the boxplot
            fillcolor = "rgba(0,0,0,0)",    # Transparent fill (no fill)
            boxpoints=FALSE) %>% 
  add_markers(x = ~jitter(as.numeric(method)), y = ~pct_traj, color = ~factor(nrep),
              marker = list(size = 6),
              hoverinfo = "text",
              text = ~paste0("method: ",method,
                             "<br>pct<t: ",round(pct_traj, 3),
                             "<br>exp_seed: ", exp_seed,
                             "<br>init_npar: ", init_npar,
                             "<br>nrep: ", nrep,
                             "<br>grid_npar: ", grid_npar,
                             "<br>nTS_samp: ", nTS_samp
                             ),
              showlegend = FALSE) %>% 
  layout(legend = list(orientation = "h",
                       x =0.5, xanchor = "center",
                       y = 1, yanchor = "bottom"
                       ),
        xaxis = list(title = "Method",
                      tickmode = "array",
                      tickvals = as.numeric(unique(b700$method)),  # Numeric x-values
                      ticktext = unique(b700$method),  # Corresponding categorical labels
                      showticklabels = TRUE))

```


```{r}
ggplot(threshold_cnt, aes(x=exp_seed,y=pct_traj, colour=method)) +
  stat_smooth(method="loess", se=TRUE, aes(fill=method), alpha=0.3) +
  facet_grid(sim_budget~threshold) +
  theme_bw()

ggplot(threshold_cnt, aes(x=factor(nrep),y=pct_traj, colour=method)) +
  geom_boxplot() +
  facet_grid(sim_budget~threshold) +
  theme_bw()
```

```{r, fig.width=5}
# Ensure pct_cat is a factor for coloring
t = 25
threshold_cnt %>%
  filter(threshold == t) %>%
  pivot_longer(cols = c(init_npar, nrep, grid_npar, nTS_samp), names_to = "parameter", values_to = "val") %>%
  ggplot(aes(x = factor(val), y = pct_traj, fill = method)) +
  geom_boxplot(outlier.shape = NA, color = "black") +  # Black outline, no default outliers
  ylab('Prop. of budget under threshold') +
  xlab('Parameter value') +
  facet_grid(sim_budget~parameter, scales='free_x')  +
  ggtitle(paste('Threshold =', t)) +
  theme_minimal()
  # Facet by variable
  #labs(x = "Parameter Values", y = "pct_traj", title = "Boxplots of pct_traj by Parameters") +
  #theme_minimal() +
  #theme(legend.position = "right")

```


Dig into this more, e.g., the budget 200 with 60% good what was up, 

```{r}
checkpoint_reached
```


```{r message=FALSE, warning=FALSE}
checkpoint_reached$proportion_checkpointed = ifelse(checkpoint_reached$checkpoint==-1, 0, 1)

ggplot(checkpoint_reached, aes(x=threshold, y=proportion_checkpointed, fill=method)) + 
  geom_bar(stat='summary', position="dodge") + 
  facet_wrap(~n_trajectories + sim_budget, labeller = labeller(n_trajectories = function(x) paste(x, 'trajectories'), sim_budget = function(x) paste('budget=', x))) +
  theme_minimal()
```

```{r}
checkpoint_reached$method = factor(checkpoint_reached$method)

checkpoint_reached %>% 
  filter(sim_budget==700, threshold==15) %>%
  plot_ly() %>% 
  add_trace(x = ~as.numeric(method), y = ~checkpoint, type = "box", 
              hoverinfo = 'name+y',
              line = list(color = "black"),   # Black outline for the boxplot
              fillcolor = "rgba(0,0,0,0)",    # Transparent fill (no fill)
              boxpoints=FALSE) %>% 
    add_markers(x = ~jitter(as.numeric(method)), y = ~checkpoint, color = ~nrep,
                marker = list(size = 6),
                hoverinfo = "text",
                text = ~paste0("method: ",method,
                               "<br>pct<t: ",round(checkpoint, 3),
                               "<br>exp_seed: ", exp_seed,
                               "<br>init_npar: ", init_npar,
                               "<br>nrep: ", nrep,
                               "<br>grid_npar: ", grid_npar,
                               "<br>nTS_samp: ", nTS_samp
                               ),
                showlegend = FALSE) %>% 
    layout(legend = list(orientation = "h",
                         x =0.5, xanchor = "center",
                         y = 1, yanchor = "bottom"
                         ),
          xaxis = list(title = "Method",
                        tickmode = "array",
                        tickvals = as.numeric(unique(b700$method)),  # Numeric x-values
                        ticktext = unique(b700$method),  # Corresponding categorical labels
                        showticklabels = TRUE))
```

```{r, fig.width=5}
ggplot(checkpoint_reached %>% filter(threshold==20, n_trajectories==50))+
  geom_density(aes(x=checkpoint, fill=factor(nrep)), alpha=.4) +
  facet_grid(sim_budget~method, scales="free_y")
    
```


```{r}
ggplot(threshold_budget_path %>% filter(exp_id==100), aes(x=time, y=trajectories_found, color=method, group=method)) + 
  #stat_smooth(method="loess", se=TRUE, aes(fill=method), alpha=0.3)  + 
  geom_line() +
  facet_wrap(~threshold, ncol=4) + 
  theme_minimal()

```

Why is purple higher than green? Why is blue so low?
```{r message=FALSE, warning=FALSE, fig.width=5, fig.height=2}
ggplot(threshold_budget_auc, aes(x=threshold, y=auc, fill=method)) + 
  geom_bar(stat="summary", position="dodge") + 
  geom_errorbar(stat='summary', position="dodge") +
  facet_wrap(~sim_budget, labeller = labeller(sim_budget = function(x) paste('budget=', x)), scale='free_y')+
  theme_minimal()
```


```{r}
threshold_budget %>%
    group_by(method, threshold) %>%
    summarise(
        n =n(), 
        mean_auc = mean(auc),
        std = sd(auc),
        lower_ci = mean_auc - qt(0.975, df=n()-1) * sd(auc) / sqrt(n()),
        upper_ci = mean_auc + qt(0.975, df=n()-1) * sd(auc) / sqrt(n())
    )

```
```{r}
pm <- ggpairs(
  idk[,3:ncol(idk)],
  mapping = ggplot2::aes(color = cut),
  upper = list(continuous = wrap("density", alpha = 0.5), combo = "box_no_facet"),
  lower = list(continuous = wrap("points", alpha = 0.3), combo = wrap("dot_no_facet", alpha = 0.4)),
  title = "Diamonds"
)
```


```{r}
# Convert to long format for ggplot
df_long <- reshape2::melt(idk[,3:ncol(idk)], id.vars = "auc")

ggplot(df_long, aes(value, auc)) +
  geom_point(aes(color = auc)) +
  facet_wrap(~ variable, scales = "free") +
  scale_color_viridis_c()
```

```{r message=FALSE, warning=FALSE}
idk = threshold_budget %>% filter(method=='adaptive_crn', threshold==15)
idk = idk %>%
    mutate(auc_category = cut(auc, 
                              breaks = quantile(auc, probs = seq(0, 1, 0.2), na.rm = TRUE),
                              labels = c("Very Low", "Low", "Medium", "High", "Very High"),
                              include.lowest = TRUE))

ggpairs(idk, columns=5:10, mapping = aes(color = auc_category)) + 
  scale_color_manual(values = c("blue", rep("purple", 4), "red")) 
```


```{r}
ggplot(threshold_budget, aes(x=threshold, y=auc, fill=method)) + 
  geom_bar(stat="summary", fun="mean", position="dodge") + 
  geom_errorbar(stat="summary", fun.data=mean_sdl, fun.args=list(mult=1), position="dodge")

```



  

  
```{r}
dff = dfx %>% filter(iter > 1, method %in% c('fixed_crn', 'fixed_het')) %>% group_by(method, p1, p2) %>% count(sort=TRUE) %>% mutate(logn=log(n))

ggplot(dff)+ 
  geom_point(aes(x = p1, y = p2, color=n), size=5) +
  geom_point(data=data.frame(p1=par_true[1], p2=par_true[2], rep=par_true[3]), aes(x=p1, y=p2), color='red', fill='red', size=3, shape=23) +
  facet_wrap(~method) +
  theme_minimal() 
  
```
  
```{r}
ggplot(dfx, aes(x = p1, y = p2, color=rmse)) +
  geom_density_2d_filled(alpha = 0.5) +
  facet_wrap(~method) +
  theme_minimal() 
```





```{r}


ggplot(dfx, aes(x = p1, y = p2, color=rmse)) +
  geom_point(size=3, alpha=.5) + 
 #scale_color_gradient(low = "gold", high = "cornflowerblue") +
  theme_minimal() 
  #geom_density_2d_filled(alpha = 0.5)
```



```{r}
  n <- ncol(simout)
  m <- nrow(simout)
  
  # Compute the first term: Average distance from surveillance data
  fitness <- mean(sqrt(colSums((simout - matrix(yobs, nrow = m, ncol = n))^2)))
  
  # Compute the second term: Average pairwise distance between trajectories
  pairwise_distances <- function(a, b) {
    sqrt(sum((a - b)^2))
  }
  
  pairwise <- 0
  for (i in 1:n) {
    for (j in 1:n) {
      pairwise <- pairwise + sqrt(sum(simout[,i] - simout[,j])^2)
    }
  }
  pairwise <- pairwise/(2*n^2)

```


```{r}
  n <- ncol(simout)
  m <- nrow(simout)
  
  # Compute the first term: Average distance from surveillance data
  fitness <- 0
  for (i in 1:n) {
    fitness <- fitness + sqrt(sum(simout[,i] - yobs)^2)
  }
  fitness <- fitness/n
  
  #mean(sqrt(colSums((simout - matrix(yobs, nrow = m, ncol = n))^2)))
  
  # Compute the second term: Average pairwise distance between trajectories
  pairwise_distances <- function(a, b) {
    sqrt(sum((a - b)^2))
  }
  
  pairwise <- 0
  for (i in 1:n) {
    for (j in 1:n) {
      pairwise <- pairwise + sqrt(sum(simout[,i] - simout[,j])^2)
    }
  }
  pairwise <- pairwise/(2*n^2)
```


```{r}
energy_score <- function(simout, yobs) {
  n <- ncol(simout)
  m <- nrow(simout)
  
  # Compute the first term: Average distance from surveillance data
  fitness <- 0
  for (i in 1:n) {
    fitness <- fitness + sqrt(sum(simout[,i] - yobs)^2)
  }
  fitness <- fitness/n
  
  #mean(sqrt(colSums((simout - matrix(yobs, nrow = m, ncol = n))^2)))
  
  # Compute the second term: Average pairwise distance between trajectories
  pairwise_distances <- function(a, b) {
    sqrt(sum((a - b)^2))
  }
  
  pairwise <- 0
  for (i in 1:n) {
    for (j in 1:n) {
      pairwise <- pairwise + sqrt(sum(simout[,i] - simout[,j])^2)
    }
  }
  pairwise <- pairwise/(2*n^2)
  return(fitness-pairwise)
}
```


# Example usage:
set.seed(42)
N <- 100  # Number of samples
M <- 10   # Number of time steps

# Simulate some trajectory samples (N x M matrix)
x_samples <- matrix(rnorm(N * M, mean = 0, sd = 1), nrow = N, ncol = M)

# Simulated observed trajectory
y_observed <- rnorm(M, mean = 0, sd = 1)

# Compute Energy Score
ES_value <- energy_score(x_samples, y_observed)
print(ES_value)
```


```{r}
threshold_budget(out_list, show_plots=TRUE)
```


```{r}
nbests <- c(10, 25, 50, 75, 100)

combine_nbests <- function(out_list, nbests) {
  all_results <- list()
  for (i in seq_along(nbests)) {
    result <- lapply(out_list, function(out) nbest_mean(nbest = nbests[[i]], out = out))
    result$nbest <- nbests[[i]]
    all_results[[i]] <- result
  }
  
  
  combined_df <- do.call(rbind, lapply(all_results, function(x) {
    df <- as.data.frame(x)
    return(df)
  }))
  
  return(combined_df)
}


analyze_exp <- function(exp_id, exp_path, nbest_list=c(10, 25, 50, 75, 100)){
  out_list <- load_outputs(exp_id, exp_path)
  df <- combine_nbests(out_list, nbest_list)
  df$exp_id <- exp_id
  return(df)
}
```


```{r message=FALSE, warning=FALSE}
exp_list <- 1:990

result_df <- do.call(rbind, lapply(exp_list, function(x) {
    df <- analyze_exp(x, exp_path=exp_path)
    return(df)
  }))
```





```{r}
out_list <- load_outputs(1, exp_path)
nbest_pct(25, out_list$adaptive_crn$y_rmse, 25)

plot(1:20, nbest_pct(25, out_list$adaptive_crn$y_rmse, 25)$)
```


```{r}
plot_nbest_traj(100, out_list$fixed_crn, out_list$adaptive_crn, ytrue)
```


```{r}
result_df['best_method'] = apply(result_df[, 1:4], 1, which.min)
result_df$best_method <- colnames(result_df)[result_df$best_method]
table(result_df$best_method,result_df$nbest)
```



```{r}
melted_df <- result_df %>%
  pivot_longer(
    cols = c("fixed_crn", "adaptive_crn", "fixed_het",  "adaptive_het"),
    names_to = "method",
    values_to = "rmse"
  )
```

Merge in configs:
```{r}
exp_config <- read.csv("/lcrc/project/EMEWS/improv/abby/adaptiveTS/emews/data/upfs/config.csv")
exp_config <- exp_config[, -ncol(exp_config)]
exp_config$exp_id <- as.numeric(gsub("exp_", "", exp_config$exp_id))

df <- merge(melted_df, exp_config)

df
```



```{r}
ggplot(melted_df, aes(x=factor(nbest), y=rmse, fill=method)) + 
  geom_boxplot(position = position_dodge(width = 0.8))+
  theme_bw()

ggplot(melted_df, aes(x=factor(nbest), y=rmse, fill=method)) + 
  geom_bar(stat="summary", position="dodge") +
  geom_errorbar(stat='summary', position="dodge") +
  theme_minimal()
```



```{r message=FALSE, warning=FALSE}
ggplot(df, aes(x=factor(sim_budget), y=rmse, fill=method)) + 
  geom_bar(stat="summary", position="dodge") +
  geom_errorbar(stat='summary', position="dodge") +
  facet_wrap(~factor(nbest), ncol=5) +
  theme_minimal()

ggplot(df, aes(x=factor(init_npar), y=rmse, fill=method)) + 
  geom_bar(stat="summary", position="dodge") +
  geom_errorbar(stat='summary', position="dodge") +
  facet_wrap(~factor(nbest), ncol=5) +
  theme_minimal()
```

```{r message=FALSE, warning=FALSE}
ggplot(df, aes(x=sim_budget, y=rmse, fill=method, color=method)) + 
  geom_point(stat="summary", position="dodge") +
  geom_line(aes(x=sim_budget, y=rmse, color=method)) + 
  #geom_errorbar(stat='summary', position="dodge") +
  facet_wrap(~factor(nbest)) +
  theme_minimal()
```



```{r}
ggplot(df, aes(x=factor(exp_seed), y=rmse, fill=method)) + 
  geom_bar(stat="summary", position="dodge") +
  geom_errorbar(stat='summary', position="dodge") +
  theme_bw()
```



```{r}
ggplot(df, aes(x = factor(init_npar), y = rmse, fill = method)) +
    geom_boxplot(position = position_dodge(width = 0.8)) +
    theme_minimal()
```


```{r}
df %>% filter(nbest==25, sim_budget==200) %>%
  group_by(method, init_npar) %>%
  summarize(rmse = mean(rmse))

```


Just do the AUC for the two  metrics:
```{r}
nbest_pct(100, out$fixed_het$y_rmse, 100)
```


```{r}

auc_trapezoids<- function(y){
  x <- seq_along(y)
  # want zero to be reference
  auc <- sum((y[-1] + y[-length(y)]) * diff(x) / 2)
  return(auc)
}



exp_id <- 5

outfile <- sprintf("%s/exp_%s_out.RData", exp_path, exp_id)

temp_env <- new.env()
load(outfile, envir = temp_env)
out_fixed_CRNGP <- temp_env$out_fixed_CRNGP
out_adaptive_CRNGP <- temp_env$out_adaptive_CRNGP
out_fixed_hetGP <- temp_env$out_fixed_hetGP
out_adaptive_hetGP <- temp_env$out_adaptive_hetGP

res_fixed_CRNGP <- collect_results(out_fixed_CRNGP)
res_adaptive_CRNGP <- collect_results(out_adaptive_CRNGP)
res_fixed_hetGP <- collect_results(out_fixed_hetGP)
res_adaptive_hetGP <- collect_results(out_adaptive_hetGP)

  y_fixed_crn <- res_fixed_CRNGP$y_native
  y_adapt_crn <-  res_adaptive_CRNGP$y_native
  y_fixed_het <-  res_fixed_hetGP$y_native
  y_adapt_het <-  res_adaptive_hetGP$y_native
  
  
  # negative makes auc weird

  
  #y_fixed_crn <- y_fixed_crn - ymin
  #y_adapt_crn <- y_adapt_crn - ymin
  #y_fixed_het <- y_fixed_het - ymin
  #y_adapt_het <- y_adapt_het - ymin
  
  res_fixed_crn <- best_so_far(y_fixed_crn, m=nbest, n=n)
  res_adaptive_crn <- best_so_far(y_adapt_crn, m=nbest, n=n)
  res_fixed_het <- best_so_far(y_fixed_het, m=nbest, n=n)
  res_adaptive_het <- best_so_far(y_adapt_het, m=nbest, n=n)
  
   ymin <- min(res_fixed_crn, res_adaptive_crn, res_fixed_het, res_adaptive_het)
  ymax <- max(res_fixed_crn, res_adaptive_crn, res_fixed_het, res_adaptive_het)
  
  labs = c("CRN-adaptive", "CRN-fixed", "Het-adaptive", "Het-fixed")
  xax_fixed_crn = (1:length(res_fixed_crn)) + n
  xax_adapt_crn = (1:length(res_adaptive_crn)) + n
  xax_fixed_het = (1:length(res_fixed_het)) + n
  xax_adapt_het = (1:length(res_adaptive_het)) + n
  
  plot(xax_adapt_crn, res_adaptive_crn, pch = 19, col = alpha("#F8766D", 01), type = "l", 
     xlab = "budget", ylab = paste("mse of best", nbest), main = paste("Experiment", exp_id))
  points(xax_fixed_crn, res_fixed_crn, pch = 19, col = alpha("#00BA38", 1), type = "l")
  points(xax_adapt_het, res_adaptive_het, pch = 19, col = alpha("#4287f5", 1), type = "l")
  points(xax_fixed_het, res_fixed_het, pch = 19, col = alpha("#f5c842", 1), type = "l")
  legend("topright", labs, pch = 19, lty = 1, col = c("#F8766D", "#00BA38", "#4287f5", "#f5c842"))

  
  auc_fixed_crn <- auc_trapezoids(res_fixed_crn)
  auc_adapt_crn <- auc_trapezoids(res_adaptive_crn)
  auc_fixed_het <- auc_trapezoids(res_fixed_het)
  auc_adapt_het <- auc_trapezoids(res_adaptive_het)
  
  auc_out <- list(auc_fixed_crn=auc_fixed_crn,
               auc_adapt_crn=auc_adapt_crn,
               auc_fixed_het=auc_fixed_het,
               auc_adapt_het=auc_adapt_het,
               #auc_delta=(auc_adapt-auc_fixed)/auc_fixed,
               auc_fixed_crn_pct = auc_fixed_crn/((ymax-ymin) * length(res_fixed_crn)),
               auc_adaptive_crn_pct = auc_adapt_crn/((ymax-ymin) * length(res_adaptive_crn)),
               auc_fixed_het_pct = auc_fixed_het/((ymax-ymin) * length(res_fixed_het)),
               auc_adaptive_het_pct = auc_adapt_het/((ymax-ymin) * length(res_adaptive_het)))
```


```{r}
for(ii in c(10, 30, 50, 80, 100)){
  print(plot_nbest_traj(nbest = ii, 
                        res_fixed_CRNGP$x_mat, 
                        res_adaptive_CRNGP$x_mat, 
                        res_fixed_CRNGP$y_vec, 
                        res_adaptive_CRNGP$y_vec, 
                        yobs = ytrue_vec))
  # print(err_hist(nbest = ii, y_fixed_native, y_adaptive_native))
}
```


```{r, fig.width=14, fig.height=7}
nbests <- seq(20, sim_budget, length.out = 6)
par(mfrow = c(2, 3))
for(nbest in nbests){
  plot_pct_traj2(nbest, res_adaptive_CRNGP$y_native, res_fixed_CRNGP$y_native, labs = c("CRN-adaptive", "CRN-fixed"))
}
```


```{r}
## Create ground truth
par_true <- c(0.45, 0.35, 50)
xtrue <- par_true[1:2]
strue <- par_true[3]
ytrue <- run_sim(c(xtrue, strue))
ytrue_full <- ytrue$n_SI
ytrue_vec <- ytrue_full


# user input
exp_path <- "~/argonne/projects/data_assimilation/adaptiveTS/experiments/exp_1/"
exp_seed <- 23
init_npar <- 5
nrep <- 10
sim_budget <- 200
grid_npar <- 100
nTS_samp <- 30

# optional input
err_sig <- 0.5
prop_sig <- 0.3

# fixed input for these experiments
sim_func <- run_sim_err
p <- 2
ref <- -2
```


```{r}
out_fixed_CRNGP <- TSBatchBO_CRNGP(init_npar, nrep, p, sim_budget = sim_budget, 
                                   grid_npar = grid_npar, nTS_samp = nTS_samp, 
                                   ytrue = ytrue_full, ref = ref,
                                   err_sig = err_sig, prop_sig = prop_sig, 
                                   sim_func = run_sim_err, exp_seed = exp_seed, covtype = "Matern5_2",
                                   adaptive = F)

out_adaptive_CRNGP <- TSBatchBO_CRNGP(init_npar, nrep, p, sim_budget = sim_budget, 
                                      grid_npar = grid_npar, nTS_samp = nTS_samp, 
                                      ytrue = ytrue_full, ref = ref,
                                      err_sig = err_sig, prop_sig = prop_sig, 
                                      sim_func = run_sim_err, exp_seed = exp_seed, covtype = "Matern5_2",
                                      adaptive = T)

out_fixed_hetGP <- TSBatchBO_hetGP(init_npar, nrep, p, sim_budget = sim_budget, 
                                   grid_npar = grid_npar, nTS_samp = nTS_samp, 
                                   ytrue = ytrue_full, ref = ref,
                                   err_sig = err_sig, prop_sig = prop_sig, 
                                   sim_func = run_sim_err, exp_seed = exp_seed, covtype = "Matern5_2",
                                   adaptive = F)

out_adaptive_hetGP <- TSBatchBO_hetGP(init_npar, nrep, p, sim_budget = sim_budget, 
                                      grid_npar = grid_npar, nTS_samp = nTS_samp, 
                                      ytrue = ytrue_full, ref = ref,
                                      err_sig = err_sig, prop_sig = prop_sig, 
                                      sim_func = run_sim_err, exp_seed = exp_seed, covtype = "Matern5_2",
                                      adaptive = T)

```


```{r}
## collect and format results
collect_results <- function(out_list){
  x_mat <- do.call(rbind, out_list$X_list)
  y_vec <- unlist(out_list$y_list)
  y_native <- unlist(out_list$ynative_list)
  
  simout_flat <- do.call(c,out_list$simout_list)
  simout_mat <- do.call(cbind, lapply(simout_flat, function(df) df$n_SI))
  
  return(list(x_mat=x_mat, 
              y_vec=y_vec, 
              y_native=y_native, 
              simout_mat=simout_mat))
}

res_fixed_CRNGP <- collect_results(out_fixed_CRNGP)
res_adaptive_CRNGP <- collect_results(out_adaptive_CRNGP)
res_fixed_hetGP <- collect_results(out_fixed_hetGP)
res_adaptive_hetGP <- collect_results(out_adaptive_hetGP)
```


```{r}
x_list <- out_fixed_CRNGP$X_list
plot(x_list[[1]][,1:2], col=alpha(rgb(0,0,0), 0.5))
points(0.45, 0.35, col='blue')
for(i in 2:length(x_list)){
  points(x_list[[i]][,1:2], col=alpha(rgb(0,0,0), 0.5))
}

```


```{r}
pairs_plot(res_fixed_CRNGP$x_mat,
           res_adaptive_CRNGP$x_mat,
           res_fixed_hetGP$x_mat,
           res_adaptive_hetGP$x_mat)
```

```{r}
for(ii in c(10, 30, 50, 80, 100)){
  print(plot_nbest_traj(nbest = ii, 
                        res_fixed_CRNGP$x_mat, 
                        res_adaptive_CRNGP$x_mat, 
                        res_fixed_CRNGP$y_vec, 
                        res_adaptive_CRNGP$y_vec, 
                        yobs = ytrue_vec))
  # print(err_hist(nbest = ii, y_fixed_native, y_adaptive_native))
}
```
```{r, fig.width=14, fig.height=7}
nbests <- seq(20, sim_budget, length.out = 6)
par(mfrow = c(2, 3))
for(nbest in nbests){
  plot_pct_traj2(nbest, res_adaptive_CRNGP$y_native, res_fixed_CRNGP$y_native, labs = c("CRN-adaptive", "CRN-fixed"))
}
```

```{r}
best_so_far <- function(v, m=10, n=50){
  # m is number of best points to aggregate over
  # n is number of initial designs (not factoring into performance)

  # Initialize a result vector to store means
  result <- numeric(length(v) - n + 1)
  
  # Loop through all indices from n to N
  for (i in n:length(v)) {
    # Extract the subset of the vector starting from the current index i
    subset_v <- v[1:i]
    
    # Get the m smallest elements from the subset
    m_smallest <- sort(subset_v)[1:min(m, length(subset_v))]
    
    # Calculate the mean of the m smallest elements
    result[i - n + 1] <- mean(m_smallest)
  }
  return(result)
}


n = 50
nbest = 10

res_fixed <- best_so_far(res_fixed_CRNGP$y_native, m=nbest, n=n)
res_adaptive <- best_so_far(res_adaptive_CRNGP$y_native, m=nbest, n=n)
res_fixed_het <- best_so_far(res_fixed_hetGP$y_native, m=nbest, n=n)
res_adaptive_het <- best_so_far(res_adaptive_hetGP$y_native, m=nbest, n=n)

labs = c("CRN-adaptive", "CRN-fixed")
xax_fixed = (1:length(res_fixed)) + n
xax_adapt = (1:length(res_adaptive)) + n

plot(xax_adapt, res_adaptive, pch = 19, col = alpha("#F8766D", 01), type = "l", 
     xlab = "budget", ylab = paste("mse of best", nbest), main = paste("nbest = ", nbest))
points(xax_fixed, res_fixed, pch = 19, col = alpha("#00BA38", 1), type = "l")
legend("topright", labs, pch = 19, lty = 1, col = c("#F8766D", "#00BA38"))

```


```{r}
best_so_far <- function(v, m=10, n=50){
  # m is number of best points to aggregate over
  # n is number of initial designs (not factoring into performance)

  # Initialize a result vector to store means
  result <- numeric(length(v) - n + 1)
  
  # Loop through all indices from n to N
  for (i in n:length(v)) {
    # Extract the subset of the vector starting from the current index i
    subset_v <- v[1:i]
    
    # Get the m smallest elements from the subset
    m_smallest <- sort(subset_v)[1:min(m, length(subset_v))]
    
    # Calculate the mean of the m smallest elements
    result[i - n + 1] <- mean(m_smallest)
  }
  return(result)
}


```


```{r}
config <- read.csv('../experiments/config.csv')

best_so_far <- function(v, m=10, n=50){
  # m is number of best points to aggregate over
  # n is number of initial designs (not factoring into performance)

  # Initialize a result vector to store means
  result <- numeric(length(v) - n + 1)
  
  # Loop through all indices from n to N
  for (i in n:length(v)) {
    # Extract the subset of the vector starting from the current index i
    subset_v <- v[1:i]
    
    # Get the m smallest elements from the subset
    m_smallest <- sort(subset_v)[1:min(m, length(subset_v))]
    
    # Calculate the mean of the m smallest elements
    result[i - n + 1] <- mean(m_smallest)
  }
  return(result)
}

auc_trapezoids<- function(y){
  x <- seq_along(y)
  # want zero to be reference
  
  auc <- sum((y[-1] + y[-length(y)]) * diff(x) / 2)
  return(auc)
}


n <- 50
nbest <- 10

```

```{r}
load(sprintf("../experiments/experiments/exp_%d/out.RData", 1))
y_fixed_crn <- unlist(out_fixed_CRNGP[[2]])
y_adapt_crn <- unlist(out_adaptive_CRNGP[[2]])
y_fixed_het <- unlist(out_fixed_hetGP[[2]])
y_adapt_het <- unlist(out_adaptive_hetGP[[2]])
```

```{r}
exp <- 1
exp_auc <- function(exp, n, nbest){
  load(sprintf("../experiments/experiments/exp_%d/out.RData", exp))
  
  y_fixed_crn <- unlist(out_fixed_CRNGP[[2]])
  y_adapt_crn <- unlist(out_adaptive_CRNGP[[2]])
  y_fixed_het <- unlist(out_fixed_hetGP[[2]])
  y_adapt_het <- unlist(out_adaptive_hetGP[[2]])
  
  
  # negative makes auc weird
  ymin <- min(y_fixed_crn, y_adapt_crn, y_fixed_het, y_adapt_het)
  ymax <- max(y_fixed_crn, y_adapt_crn, y_fixed_het, y_adapt_het)
  
  y_fixed_crn <- y_fixed_crn - ymin
  y_adapt_crn <- y_adapt_crn - ymin
  y_fixed_het <- y_fixed_het - ymin
  y_adapt_het <- y_adapt_het - ymin
  
  res_fixed_crn <- best_so_far(y_fixed_crn, m=nbest, n=n)
  res_adaptive_crn <- best_so_far(y_adapt_crn, m=nbest, n=n)
  res_fixed_het <- best_so_far(y_fixed_het, m=nbest, n=n)
  res_adaptive_het <- best_so_far(y_adapt_het, m=nbest, n=n)
  
  labs = c("CRN-adaptive", "CRN-fixed", "Het-adaptive", "Het-fixed")
  xax_fixed_crn = (1:length(res_fixed_crn)) + n
  xax_adapt_crn = (1:length(res_adaptive_crn)) + n
  xax_fixed_het = (1:length(res_fixed_het)) + n
  xax_adapt_het = (1:length(res_adaptive_het)) + n
  
  plot(xax_adapt_crn, res_adaptive_crn, pch = 19, col = alpha("#F8766D", 01), type = "l", 
     xlab = "budget", ylab = paste("mse of best", nbest), main = paste("Experiment", exp))
  points(xax_fixed_crn, res_fixed_crn, pch = 19, col = alpha("#00BA38", 1), type = "l")
  points(xax_adapt_het, res_adaptive_het, pch = 19, col = alpha("#4287f5", 1), type = "l")
  points(xax_fixed_het, res_fixed_het, pch = 19, col = alpha("#f5c842", 1), type = "l")
  legend("topright", labs, pch = 19, lty = 1, col = c("#F8766D", "#00BA38", "#4287f5", "#f5c842"))

  
  auc_fixed_crn <- auc_trapezoids(res_fixed_crn)
  auc_adapt_crn <- auc_trapezoids(res_adaptive_crn)
  auc_fixed_het <- auc_trapezoids(res_fixed_het)
  auc_adapt_het <- auc_trapezoids(res_adaptive_het)
  
  auc_out <- list(auc_fixed_crn=auc_fixed_crn,
               auc_adapt_crn=auc_adapt_crn,
               auc_fixed_het=auc_fixed_het,
               auc_adapt_het=auc_adapt_het,
               #auc_delta=(auc_adapt-auc_fixed)/auc_fixed,
               auc_fixed_crn_pct = auc_fixed_crn/(ymax * length(res_fixed_crn)),
               auc_adaptive_crn_pct = auc_adapt_crn/(ymax * length(res_adaptive_crn)),
               auc_fixed_het_pct = auc_fixed_het/(ymax * length(res_fixed_het)),
               auc_adaptive_het_pct = auc_adapt_het/(ymax * length(res_adaptive_het)))
  return(auc_out)
}

```


```{r}
exp_auc(1, n=n, nbest=nbest)
```

```{r}
par(mfrow = c(1, 3))
for(nbest in c(10, 20, 50)){
  exp_auc(1, n=n, nbest=nbest)
}

```



```{r}
BASE_DIR <- "/lcrc/project/EMEWS/afadikar/git/adaptiveTS/experiments/"
exp_seed <- 1
init_npar <- c(5, 10)
nrep <- c(10, 20)
sim_budget <- c(200, 400, 600)
grid_npar <- c(100, 200)
nTS_samp <- c(10, 20, 30)


d <- expand.grid(exp_seed, init_npar, nrep, sim_budget, grid_npar, nTS_samp)
colnames(d) <- c("exp_seed", "init_npar", "nrep", "sim_budget", "grid_npar", "nTS_samp")

d_eff <- d[d$init_npar * d$nrep < d$sim_budget, ]
d_eff$exp_id <- paste0("exp_", 1:nrow(d_eff))

d_eff <- d_eff[, c(7, 1:6)]
d_eff$exp_path <- paste0(BASE_DIR, d_eff$exp_id, "/")
```


```{r}
result <- do.call(rbind, lapply(1:66, function(x) {
  output <- exp_auc(x, n, nbest=10)  # Get the named list
  c(exp_id = sprintf("exp_%d", x), output)      # Combine the input with the list
}))

# Convert to a data.frame
result_df <- as.data.frame(result, stringsAsFactors = FALSE)
```
```{r}
result_df <- as.data.frame(merge(d_eff, result_df))
```


```{r}
library(tidyr)
cols <-  c("init_npar","nrep","sim_budget","grid_npar","nTS_samp", "auc_fixed_crn_pct","auc_adaptive_crn_pct", "auc_fixed_het_pct","auc_adaptive_het_pct")

melted_df <- result_df[,cols] %>%
  pivot_longer(
    cols = c("auc_fixed_crn_pct", "auc_adaptive_crn_pct", "auc_fixed_het_pct","auc_adaptive_het_pct"),
    names_to = "method",
    values_to = "auc_value"
  )

melted_df$auc = unlist(melted_df$auc_value)
melted_df$method <- sub("auc_", "", melted_df$method)
```



```{r}
ggplot(melted_df, aes(x = factor(init_npar), y = auc, fill = method)) +
    geom_boxplot(position = position_dodge(width = 0.8)) +
    theme_minimal()

ggplot(melted_df, aes(x = factor(nrep), y = auc, fill = method)) +
    geom_boxplot(position = position_dodge(width = 0.8)) +
    theme_minimal()

ggplot(melted_df, aes(x = factor(sim_budget), y = auc, fill = method)) +
    geom_boxplot(position = position_dodge(width = 0.8)) +
    theme_minimal()

ggplot(melted_df, aes(x = factor(grid_npar), y = auc, fill = method)) +
    geom_boxplot(position = position_dodge(width = 0.8)) +
    theme_minimal()

ggplot(melted_df, aes(x = factor(nTS_samp), y = auc, fill = method)) +
    geom_boxplot(position = position_dodge(width = 0.8)) +
    theme_minimal()
```

```{r}
par(mfrow = c(3, 2))

ggplot(melted_df, aes(x = factor(init_npar), y = auc, fill = method)) +
    geom_bar(stat="identity", position="dodge") +
    theme_minimal()

ggplot(melted_df, aes(x = factor(nrep), y = auc, fill = method)) +
    geom_bar(stat="identity", position="dodge") +
    theme_minimal()

ggplot(melted_df, aes(x = factor(sim_budget), y = auc, fill = method)) +
    geom_bar(stat="identity", position="dodge") +
    theme_minimal()

ggplot(melted_df, aes(x = factor(grid_npar), y = auc, fill = method)) +
    geom_bar(stat="identity", position="dodge") +
    theme_minimal()

ggplot(melted_df, aes(x = factor(nTS_samp), y = auc, fill = method)) +
    geom_bar(stat="identity", position="dodge") +
    theme_minimal()
```


```{r}
nbest <- 20
y1 <- res_adaptive_CRNGP$y_native
y2 <- res_fixed_CRNGP$y_native
labs = c("CRN-adaptive", "CRN-fixed")
nerror_ticks=20

y_df <- data.frame(y = c(y1[order(y1)][1:nbest], 
                         y2[order(y2)][1:nbest]),
                   type = rep(labs, each = nbest))

error_ticks <- seq(0, max(y_df$y), length.out = nerror_ticks)
pctraj_1 <- pctraj_2 <- rep(NA, nerror_ticks)

for (ii in 1:nerror_ticks){
  pctraj_1[ii] <- mean(y_df$y[y_df$type == labs[1]] < error_ticks[ii])
  pctraj_2[ii] <- mean(y_df$y[y_df$type == labs[2]] < error_ticks[ii])
}

plot(error_ticks, pctraj_1, pch = 19, col = alpha("#F8766D", 01), type = "b", 
     xlab = "sum-squared-error", ylab = "% best traj", main = paste("nbest = ", nbest))
points(error_ticks, pctraj_2, pch = 19, col = alpha("#00BA38", 1), type = "b")
legend("topleft", labs, pch = 19, lty = 1, col = c("#F8766D", "#00BA38"))
```


```{r, fig.width=7, fig.height=3}
par(mfrow = c(1, 3))
area_under_curve(nbests, res_adaptive_CRNGP$y_native, res_fixed_CRNGP$y_native, labs = c("CRN-adaptive", "CRN-fixed"))
area_under_curve(nbests, res_adaptive_hetGP$y_native, res_fixed_hetGP$y_native, labs = c("het-adaptive", "het-fixed"))
area_under_curve(nbests, res_adaptive_CRNGP$y_native, res_adaptive_hetGP$y_native, labs = c("CRN-adaptive", "het-adaptive"))
```

```{r}
y1 <- res_adaptive_CRNGP$y_native
y2 <- res_fixed_CRNGP$y_native
threshold <- 200

y1 <- sqrt(y1)
y2 <- sqrt(y2)


```


```{r}
library(laGP)
x <- c(1, 2, 3, 4, 12)
y <- c(0, -1.75, -2, -0.5, 5)

gpi <- newGP(matrix(x, ncol=1), y, d=10, g=1e-8)
xx <- seq(0, 13, length=1000)
p <- predGP(gpi, matrix(xx, ncol=1), lite=TRUE)

m <- which.min(y)
fmin <- y[m]
d <- fmin - p$mean
s <- sqrt(p$s2)
dn <- d/s
ei <- d*pnorm(dn) + s*dnorm(dn)
```